---
title: "PUBS Qualtrics Data organization - Week 2"
author: ""
date: "9/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


PUBS Data Assignment Week 1: Cleaning and Organization of Survey Data 
 
The goal of this week’s assignment is to get familiar with the structure of the pilot questionnaire data from PUBS and create a standard format for the data that works well across the tasks. It’s also an opportunity to verify the pilot data so we can pay participants. For each question, justify your answer using code. 
 
The learning objectives I’m hoping you take from this first assignment are: 
(1) Loading and restructuring data in R 
(2) Very first introduction to the tidyverse/prevalent R packages in social sciences research 
(3) Exploration of possible methods for data organization 
 
 
Before you start: 
1. Download R and Rstudio: 
                  https://www.r-project.org 
                  https://www.rstudio.com/products/rstudio/download/
2. Read through the lesson on R Basics:
      Depending on your previous coding experience, this might seem painfully slow: this lesson in the bootcamp was designed for the total novice, so I really reccomend it as a starting point for people who have never coded before. Feel free to fast-forward through sections that don't seem relevant, but in terms of R basics, this should cover the most basic questions. 
      Lesson 1: https://psu-psychology.github.io/r-bootcamp-2019/talks/slow-r.html
      Other Resources: https://swirlstats.com/students.html 
                  
3. Read through the following post about Rmarkdown:
                  https://rmarkdown.rstudio.com/lesson-1.html
 


Instructions: 
Download data from Qualtrics into local directory (CSV will likely be the easiest format) and point R towards it
*Hint*, https://psu-psychology.github.io/r-bootcamp-2019/talks/slow-r.html#working_directories_and_navigation
```{r}

```

Import your downloaded CSV from qualtrics 
*Hint* https://swcarpentry.github.io/r-novice-inflammation/11-supp-read-write-csv/
```{r}

```

 
Answer the following questions about the data. Identify the code that answers each question.
How many participants are there in the dataset?
*Hint* https://psu-psychology.github.io/r-bootcamp-2019/talks/slow-r.html#indexing_data_frames

```{r}

```

How many unique subject IDs are there in the dataset? Are there any duplicate subjects?

```{r}

```

How many different measures did each of the participants complete? What are the names of the measures?
```{r}

```

How many questions are in each measure? 

Review the Secondary Document. Does this match what might be expected from the Screening Methods Document 
```{r}

```

Did the participants complete the measures? How do you know? 
If it looks like any participants are missing measures, which ones? 
```{r}

```



Most participants completed the measures. To know if participants completed the measures, there will be an answer under the columns of each question. If one is blank, then the participant didn’t complete that question. 
None of the participants are missing any measures. 


Hint: It may be helpful to make tables that summarize this information.  

