---
title: "PUBS_Assignment_Week10"
author: "Sophie Paolizzi"
date: "10/18/2021"
output: html_document
---

Scoring Conventions:  https://docs.google.com/spreadsheets/d/1V2UD28C_zAfH90BnNO3si6c0-qDUDFbHoU44rfdEt4I/edit#gid=762114925 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
options(knitr.duplicate.label = "allow")
##Load Packages and source scripts
pacman::p_load(tidyverse, readr, janitor, ggplot2,wesanderson, cowplot, flextable, plotly)
setwd("~/github_repos/PUBS_Data_Verification/") ##Set this to be whereever you're storing the data
qualtrics <- read_csv("sample_data/Qualtrics_Data_augpilot.csv")

```

```{r}
qualtrics <- qualtrics %>% dplyr::filter(!StartDate < "2021-08-30") %>% dplyr::filter(Progress == "100") #%>% dplyr::rename() ##for age
subjects <- unique(qualtrics$RandomID)
# qualtrics <- qualtrics %>% select(c(1:230, 779)) #rough way of doing this but it works
options <- "by_subject"
columns <- colnames(qualtrics)
global_vars <- (c("RandomID", "Eth", "gen", "age")) #copy names of all demographic variables in here.
```

TASK 1: Estimated time, 3 Hours. 

I'd like to see you apply the coding schemes you develop above to the data! As you can probably see looking through the data frames, many of the responses are not consistently scored as numeric or characters.Ideally, we will have all of the responses coded as numeric, to make analysis easier. 
Please have all data recoded as numeric for: PAI, STAI, PID-5, 

###PAI RECODE

```{r}

PAI <- PAI %>%
  mutate(across(
        starts_with("PAI") & ends_with(c("7","12","14","19","20","24")),
        ~recode(., "False, not at all true" = "3",
                                "Slightly True" = "2" ,
                                "Mainly True" = "1",
                                "Very True" = "0",
                .default = .)
        )) %>%
  mutate(across(
        starts_with("PAI") & !ends_with(c("7","12","14","19","20","24")),
        ~recode(., "False, not at all true" = "0",
                                "Slightly True" = "1" ,
                                "Mainly True" = "2",
                                "Very True" = "3",
                .default = .)
        ))

```

TASK 2: Set options in top chunk (line 26) to "by_subject". Run the code chunk below. 

```{r pressure, echo=FALSE}
if (options == "by_questionnaire"){
  PID <- qualtrics %>% dplyr::select(contains("PID"))
  PSWQ <- qualtrics %>% dplyr::select(contains("PSWQ"))
  PAI <- qualtrics %>% dplyr::select(contains("PAI"))
  BFAS <- qualtrics %>% dplyr::select(contains("BFAS"))
  STAI <- qualtrics %>% dplyr::select(contains("STAI"))
  global_variables <- qualtrics[,(names(qualtrics) %in% global_vars)]
  measures_list <- list(PID, PSWQ, PAI, BFAS, STAI, global_variables)
  expected_vals <- c(109, 16, 24, 20, 40, 3) 
  names(measures_list) <- c("PID", "PSWQ", "PAI", "BFAS", "STAI", "GLOBAL")
  #check expected Values
  summary_df <- as.data.frame(summary(measures_list))
  summary_df <- summary_df[1:6, c(1,3)]
  summary_df$Expected_Vals <- expected_vals 
  summary_df <- rename(summary_df, "Questionnaire" = "Var1")
  summary_df %>%
    mutate(Match = if(Freq == Expected_Vals){
      TRUE
    }else{
      FALSE
    }
)
} else if (options == "by_subject"){
  subj_list <- list()
  for (i in subjects){
  PID <- qualtrics %>% filter(RandomID == i) %>% dplyr::select(contains("PID"))
  PSWQ <- qualtrics %>% filter(RandomID == i) %>%  dplyr::select(contains("PSWQ"))
  PAI <- qualtrics %>% filter(RandomID == i) %>% dplyr::select(contains("PAI"))
  BFAS <- qualtrics %>% filter(RandomID == i) %>% dplyr::select(contains("BFAS"))
  STAI <- qualtrics %>% filter(RandomID == i) %>% dplyr::select(contains("STAI"))
  global_variables <- qualtrics[i,(names(qualtrics) %in% global_vars)]
  tmp_list <- list(PID, PSWQ, PAI, BFAS, STAI, global_variables)
  expected_vals <- c(109, 16, 24, 20, 40, 3) #PLEASE UPDATE THIS VECTOR WITH YOUR EXPECTED COUNT
  names(tmp_list) <- c("PID", "PSWQ", "PAI", "BFAS", "STAI", "GLOBAL")
  subj_list[[i]] <- tmp_list
  
  #need to do a check by subject that everything looks right - maybe want percentages? 
  summary_df <- as.data.frame(summary(tmp_list))
  summary_df <- summary_df[1:6, c(1,3)]
  summary_df$Expected_Vals <- expected_vals 
  summary_df <- rename(summary_df, "Questionnaire" = "Var1")
  summary_df %>%
    mutate(Match = if(Freq == Expected_Vals){
      TRUE
    }else{
      FALSE
    }
  summary_df$ 
  }
}
```


